%!TEX encoding = UTF8
%!TEX root =cv-llt.tex



\begin{rubric}{Relevant Experience}
%\subrubric{Awards and Achievements}
  \entry*[2023\myhori{} ] Top 2\% rank in QRT 2023 prediction challenge using \textsc{Python} data science and machine learning tools such as \texttt{numpy}, \texttt{scipy}, \texttt{pandas}, \texttt{matplotlib}, and pipelines with custom \texttt{scikit-learn} estimators; see \myurl{https://github.com/clvnkhr/Quick-notes-sk-learn/blob/master/sklearn.pdf}{write-up}.
  \entry*[2023\myhori{} ] \myurl{https://devpost.com/software/pepe-pensumperdiscere}{Attended} Anthropic AI Hackathon on building apps with Claude 2.0 LLM.
  \entry*[2023\myhori{} ] Participating in reading group on Machine Learning at the London South Bank University.
  \entry*[2023\myhori{} ] Building knowledge in finance, probability and machine learning via online courses.
  \entry*[2023\myhori{} ] Contributed to the open source \textsc{Python} tool \myurl{https://github.com/bndr/pipreqs}{\texttt{pipreqs}} and created a Neovim plugin \myurl{https://github.com/clvnkhr/macaltkey.nvim}{\texttt{macaltkey.nvim}}.
  \entry*[2023\myhori{} ] Discovered integer sequences \myurl{https://oeis.org/A364353}{\texttt{A364353}} and \myurl{https://oeis.org/A364354}{\texttt{A364354}} and added them to the \myurl{https://oeis.org/A364354}{\textsc{OEIS}}.
  % \entry*[2023] \emph{Python and Statistics for Financial Analysis}, HKUST MOOC. Completed course.
  \entry*[2022\myhori{} ] Developed skills in computer science and programming via online courses by Harvard and EPFL. 
  \entry*[2022\myhori{} ] \myurl{https://bicmr.pku.edu.cn/cn/content/show/46-2688.html}{Presented research} at the Peking University Beijing International Center for Mathematical Research. 
  \entry*[2021\myhori{} ]Led discussions on new research directions for group of about 20 researchers in fluid mechanics. 
  \entry*[2020\myhori{} ] Taught mini-course on microlocal analysis and the pseudodifferential calculus to about 20 students.
  \entry*[2020\myhori{} ] Discussed and presented important research papers in the field of theoretical PDEs to a group of about 20 researchers at Beijing Normal University.
  \entry*[2019\myhori{} ] Taught course in Advanced Partial Differential Equations, teaching rigourous proofs in advanced real analysis.
% \entry*[2022]  \myurl{https://www.coursera.org/learn/scala-functional-programming/}{\emph{Functional Programming Principles in Scala}},  \myurl{https://www.coursera.org/learn/scala-functional-program-design/}{\emph{Functional Program Design in Scala}}, \myurl{https://www.coursera.org/learn/scala-akka-reactive/}{\emph{Programming Reactive Systems}}, EPFL MOOC. Fully audited courses.
% \entry*[2022] \myurl{https://certificates.cs50.io/61d7b5aa-582d-49e7-ada4-c7cd0b965c9b.pdf?size=letter}{\emph{CS50x Introduction to Computer Science}}, Harvard University MOOC. \par Coding with \textsc{C, Python, Javascript, HTML, CSS, SQL} and \textsc{Flask}. Final project (\myurl{https://github.com/clvnkhr/tao2tex}{\texttt{tao2tex}}) on Github
% \entry*[2015] Summer internship at PwC, Malaysia.
%

%\subrubric{Certification}
%\entry*[2014] \emph{Certified XYZ Practioner}. Awarded by X Insitute.
%\entry*[2006] \emph{Certified Level 3 in ABC}. Awarded by ABC.

\end{rubric}
