\begin{rubric}{Invited talks}
%\entry*[2014 -- $\cdots\cdot$]%
%	\textbf{Community Witch,} Village of Frying Pans.
%
% Blank lines result in extra space!
%
%\entry*[2013 -- 2015]%
%	\textbf{Lecturer.} Information Technology Department, School of Engineering, Science and Technology, XYZ College.
%
\entry*[2025] Spectral cluster bounds for orthonormal functions on compact manifolds with boundary. LMS Harmonic Analysis and PDE network meeting, Loughborough. {\color{MarkerColour}\scriptsize\faLink} \url{https://sites.google.com/view/lms-hanpde-network/loughborough-autumn-2025}
\entry*[2025] Spectral cluster bounds for orthonormal functions on compact manifolds with boundary. Second Spring School and Workshop on
Spectral Theory, Fourier Analysis and PDEs, Bilbao. {\color{MarkerColour}\scriptsize\faLink} \url{https://sites.google.com/view/stfapde2025/}
%{\color{MarkerColour}\scriptsize\faLink} \url{https://www.birmingham.ac.uk/research/activity/mathematics/analysis/analysis-seminar}
\entry*[2024] Intertwining operators beyond the Stark Effect. Birmingham University Analysis Seminar.
{\color{MarkerColour}\scriptsize\faLink} \url{https://www.birmingham.ac.uk/research/activity/mathematics/analysis/analysis-seminar}
\entry*[2023] The $W^{s,p}$-boundedness of stationary wave operators for the Schr\"odinger operator with inverse-square potential. German Austrian Swiss Seminar on Analysis and PDE.

{\color{MarkerColour}\scriptsize\faLink} \url{http://www.iaa.tu-bs.de/konmerz/gausseminar/}
\entry*[2022] The $W^{s,p}$-boundedness of stationary wave operators for the Schr\"odinger operator with inverse-square potential.
 Yao Mathematical Sciences Center, Tsinghua University. 
 
{\color{MarkerColour}\scriptsize\faLink} \url{https://ymsc.tsinghua.edu.cn/en/info/1057/2518.htm}
\end{rubric}